---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# addPmData

<!-- badges: start -->
[![R-CMD-check](https://github.com/geomarker-io/addPmData/workflows/R-CMD-check/badge.svg)](https://github.com/geomarker-io/addPmData/actions)
<!-- badges: end -->

The goal of addPmData is to add PM estimates to geocoded data based on h3 geohash.

More information on the building of the PM model and creation of PM chunk files can be found [here](https://github.com/geomarker-io/st_pm_hex).

Our PM estimates are currently private, and access requires authenication through Amazon s3. Please contact us for credentials, and see our documentation for [how to set up AWS credentials in R](https://github.com/geomarker-io/s3#setting-up-aws-credentials).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("geomarker-io/addPmData")
```
## Example

```{r example}
library(addPmData)

d <- tibble::tribble(
  ~id,         ~lat,    ~lon, ~start_date,    ~end_date,
  '55000100280', 39.2, -84.6, '2008-09-09', '2008-09-11',
  '55000100281', 39.2, -84.6, '2007-08-05', '2007-08-08',
  '55000100282', 39.2, -84.6, '2015-08-31', '2015-09-02') %>%
  dplyr::mutate(dplyr::across(c(start_date, end_date), as.Date))

add_pm(d)
```
