---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# addPmData

<!-- badges: start -->
[![R-CMD-check](https://github.com/geomarker-io/addPmData/workflows/R-CMD-check/badge.svg)](https://github.com/geomarker-io/addPmData/actions)
<!-- badges: end -->

The goal of addPmData is to add PM estimates to geocoded data.

More information on the development of the spatial model can be found at the st_pm_hex repository and in the scientific manuscript describing model development: Brokamp, C. A High Resolution Spatiotemporal Fine Particulate Matter Exposure Assessment Model for the Contiguous United States. Environmental Advances. In Press. 2021. (accepted preprint available online: https://doi.org/10.1016/j.envadv.2021.100155).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("geomarker-io/addPmData")
```
## Example

```{r example}
library(addPmData)

d <- tibble::tribble(
  ~id,         ~lat,    ~lon, ~start_date,    ~end_date,
  '55000100280', 39.2, -84.6, '2008-09-09', '2008-09-11',
  '55000100281', 39.2, -84.6, '2007-08-05', '2007-08-08',
  '55000100282', 39.2, -84.6, '2015-08-31', '2015-09-02')

add_pm(d)
```
